\section{Reproducibility Details}
\label{app:repro}

\paragraph{Data preparation.} WikiText-103 is filtered to $16{,}038$ passages of length $\geq 32$ tokens; embeddings come from \texttt{all-MiniLM-L6-v2} (no dimensionality reduction; the first $384$ dims are taken as-is). HDBSCAN parameters: \texttt{min\_cluster\_size}{=}$200$, \texttt{min\_samples}{=}$5$, Euclidean metric, EOM cluster selection. The resulting cluster-size distribution is $202 / 346 / 3{,}276$ (min/median/max). $100$ triplets are sampled with seed $42$, requiring \texttt{required\_cluster\_size}{=}$150$ and $50$ texts per split; per-triplet splits are guaranteed disjoint within a triplet.

\paragraph{Unlearning hyperparameters.} GradAscent in OpenUnlearning's \texttt{wikitext\_unlearn\_tofu\_aligned.sh}: \texttt{num\_train\_epochs}{=}$5$, \texttt{per\_device\_train\_batch\_size}{=}$8$, \texttt{gradient\_accumulation\_steps}{=}$8$ (effective batch $64$), \texttt{learning\_rate}{=}$1\!\times\!10^{-5}$ with linear schedule to zero, \texttt{warmup\_steps}{=}$1$, \texttt{weight\_decay}{=}$0.01$, \texttt{paged\_adamw\_32bit}, BF16. With $|\Df|{=}50$ and effective batch $64$, exactly $5$ optimiser steps fire (one per epoch); train-loss range $[-0.84, -0.62]$.

\paragraph{Evaluation.} PPL is computed in BF16 with stride $512$ and context $1024$; each text is scored independently. Base-model PPL is cached once per (eval triplet, split) and re-used across the $100$ unlearned checkpoints. Long-format output: \texttt{ppl\_long.parquet} with one row per $(m, e, s, i)$.

\paragraph{Audit feature scripts.} \texttt{features/forget\_set.py} computes the $12$ scalars from a $50\!\times\!384$ embedding matrix in $<\!10$\,ms. Ridge regression: \texttt{sklearn.linear\_model.Ridge(alpha=1.0)} with leave-one-cluster-out grouping. Bootstrap: $10{,}000$ resamples of the $10$ LOO (true, predicted) pairs with seed $0$.

\paragraph{Hardware.} All runs on a single H100 (80\,GB) node. End-to-end wall-clock: data prep $\approx 20$ min; $100$ unlearn runs $1$\,h\,$54$ min; cross-PPL $6$\,h\,$11$ min.

\section{Additional Sanity Tables}
\label{app:tables}

\paragraph{Per-cluster monotonicity.} Across all $10$ clusters, $\Lone(c){>}\Ltwo(c){>}\Lthree(c)$ holds without exception; the smallest within-cluster gap $\Lone{-}\Ltwo$ is $0.39$ (mildest cluster) and the largest is $0.71$ (storm). Per-cluster table is included in \texttt{corruption\_summary.json}.

\paragraph{Coverage diagnostic.} The Pearson correlation between forget-set ball-coverage and $\Lthree$ is $r{=}{-}0.16$ (Spearman $\rho{=}{-}0.48$); a higher coverage of the embedding space corresponds to lower spillover, consistent with the rank-based mechanism in Sec.~\ref{sec:why-it-works}. Replacing ball coverage with a signed-projection or mutual-reachability variant is left for future work.
